Jug: Software for Reproducible Computation

### 2012-01-25 paper.tex
TXT Better introduction

\section{Introduction}
Jug is a task-based framework for Python, which supports saving and sharing of
intermediate results and parallelisation on computer clusters (or multi-core
machines).

>>>>

\section{Introduction}
The value of reproducible research in computational fields has been recognized
in several areas \citep{Vandewalle2009,Nordlie2009}. Although some of the
reports are still more forward looking rather than descriptive of current
practice, several implementations of reproducible papers (or executable papers)
have been proposed towards the goal of reproducing published analyses.

These solutions do not necessarily scale to large problems, those that take
several days, months, or years of CPU time. For very large problems,
specialized solutions are needed, but there is a range of medium-sized problems
that can be successfully tackled on a computer cluster with a few hundred nodes
or less (so that a computation that would take a CPU-year can produce results
in less than a day).

The typical ad hoc solution to this problem is to save intermediate files.
Often the design of the computation itself takes several iterations as
intermediate steps are improved. Thus, some intermediate results need to be
recomputed. This involves a great amount of human management of the state of
the computation, breaking it up into pieces, and issuing jobs on the cluster.

Jug is a task-based framework for Python, which supports saving and sharing of
intermediate results and parallelisation on computer clusters (or multi-core
machines).
